---
title: "Data"
author: "Antoinette Gambaro "
date: "(`r format(Sys.time(), '%d %B, %Y')`)"
output: 
 github_document:
   toc: TRUE
---


# Dataset 1 `beaver2`

Reynolds (1994) describes a small part of a study of the long-term temperature dynamics of beaver Castor canadensis in north-central Wisconsin. Body temperature was measured by telemetry every 10 minutes for four females, but data from a one period of less than a day for each of two animals is used there.

```{r beaver2}
library(knitr)
kable(head(beaver2))
str(beaver2)
```

## List of the variables

This data set is composed by **4 variables that are numeric**, thus we are dealing with quantitative data 

* Day
* Time 
* Temperature
* Activity

## Description of the variables 

* **day**: Day of observation (in days since the beginning of 1990) November 3–4 (beaver2).
* **time**: Time of observation, in the form 0330 for 3:30am
* **temperature**: Measured body temperature in degrees Celsius
* **activity**: Indicator of activity outside the retreat

## Reference

P. S. Reynolds (1994) Time-series analyses of beaver body temperatures. Chapter 11 of Lange, N., Ryan, L., Billard, L., Brillinger, D., Conquest, L. and Greenhouse, J. eds (1994) Case Studies in Biometry. New York: John Wiley and Sons.



# Dataset 2 `death`

Causes of death in France from 2001-2008. Variables include year, gender, cause of death, and number of deaths.

``` {r death}
library(readr)
death <- read_csv("~/Desktop/DATA SCIENCE/IntroDataScience/data/death.csv")
kable(head(death))
```

## List of the variables: 

* Time 
* Geo
* Unit
* Sex
* Age 
* Value
* ICD10

## Description of the data set

The data set is composed by **8 variables** , only one variables is continuous (TIME), the others are qualitative measure. 




## Reference

**Link**: [EUROSTAT] (http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=hlth_cd_anr&lang=en)




# Dataset 3 `TimeUse`

This data set reports how people spend their time depending on country and sex, with activities such as paid work, household and family care, etc.

``` {r TimeUse}
library(readr)
TimeUse <- read_csv("~/Desktop/DATA SCIENCE/IntroDataScience/data/TimeUse.csv")
kable(head(TimeUse))
spec(TimeUse)
```
## Description of data set 

Since there are 58 variables in the data set, I will say how many variables are qualitative measure and how many are defined as time


* **Character**: 10 variables (such as "Free time study", "Tending domestic animals", "Walking the dog", "Computer games",..)

* **Time**; 48 variables (such as  "Personal care", "Sleep", "Eating", "Other and/or unspecified personal care", "Employment",...)


## Reference 
**Link**: [EUROSTAT] (http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=tus_00week&lang=en)





