---
title: "Data Visualization"
author: "Antoinette Gambaro "
date: "(`r format(Sys.time(), '%d %B, %Y')`)"
output: 
  github_document:
    toc: TRUE 
---

# Data `gapminder` from `dslabs`:

This data set reports health and income outcomes of 184 countries from 1960 to 2016. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r packages, message=FALSE, warning=FALSE}
install.packages('dslab', repos = "http://cran.us.r-project.org")
library(dslabs)
library(ggplot2)
library(tidyverse)
library(knitr)
library(magrittr)
library(dplyr)
install.packages('ggthemes', repos = "http://cran.us.r-project.org")
library(ggthemes)
library(ggrepel)
data("gapminder")
```


## Description of the data set `gapminder`

* Country
* Year
* Infant_mortality (deaths per 1000)
* Life_expectancy (in years)
* Fertility. (Average no of children per woman)
* Population
* Gpd
* Continent
* Region

```{r }
head(kable(gapminder))
```
## Description of the variables 
the data frame contain *10545 observation* of *9 variables* 

* **factors**: Country, Continent, Region
* **numeric**: Infant_mortality, life_expectancy , Fertility, Population, Gpd. 
* **integer**; Year 


## First question

*Which is the continent that has the lowest life expectancy?*

First of all, I want to visualize the data to see the level of life expectancy in the different continents


```{r plot, warning= FALSE }
ggplot(gapminder, aes(continent,life_expectancy, fill=continent)) +
  geom_boxplot(outlier.colour="red") +
  xlab(label=" Continents") +
  ylab(label=" Life Expectancy") +
  ggtitle(label= "Life Expectancy in different Continents")

```

We can see from the box plot that the continent with the lowest life expectancy is *Africa*, whereas the rest of the continent show similar level, however Europe is slightly higher compared *America*, *Asia* and *Oceania*. 


## Second question 
*Is there a relationship between the the distribution of fertility and infant mortality in Africa?*

Since *Africa*  has the lowest level of life expectancy, I want to deep in and see the distribution infant mortality (which could be have an impact on the rate of life expectancy) in the different *region of Africa*


```{r susbset Africa }

Africa <- subset(gapminder,continent == "Africa")
ggplot(Africa, aes(infant_mortality, fill=region)) +

  geom_histogram(position = "identity")+
  stat_bin(bins = 30) +
   xlab(label= "Infant Mortality" ) +
  ylab(label="Frequency") +
  ggtitle(label= "Infant Mortality distribution in different regions of Africa")
  
```

From the histogram we can see that the infant mortality is high especially in Eastern Africa, maybe this region could be a great contributor to the fact that Africa shows a lower life expectancy compared to the other continent. 


## Reference

Irizarry, Rafael A., and Amy Gill. 2021. Dslabs: Data Science Labs. https://CRAN.R-project.org/package=dslabs.


