---
title: "Data Visualization "
author: "Antoinette Gambaro"
date: "(`r format(Sys.time(), '%d %B, %Y')`)"
output: 
  github_document:
    toc: TRUE 
--- 
# Data `gapminder` from `dslabs`

This data set reports health and income outcomes of 184 countries from 1960 to 2016. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(dslabs)
data("gapminder")
```

## Description of the data set `gapminder`

* Country
* Year
* Infant_mortality (deaths per 1000)
* Life_expectancy (in years)
* Fertility. (Average no of children per woman)
* Population
* Gpd
* Continent
* Region

```{r }
str(gapminder)
```
## Description of the variables 

The data frame contain *10545 observation* of *9 variables* 

* **factors**: Country, Continent, Region
* **numeric**: Infant_mortality, life_expectancy , Fertility, Population, Gpd. 
* **integer**; Year 

## LONG FORMAT 

Data set trasformed into a  *long format* 
```{r long}
gapminder_long <- gapminder %>% 
  pivot_longer(c("infant_mortality", "life_expectancy", "fertility", "population", "gdp"), names_to = "variable")
gapminder_long %>% head() %>% kable()
```
## UNION 

Union of *content* and *region*

```{r unite}
gapminder_long <- gapminder_long %>% 
  unite(cont_region, continent, region)
gapminder_long %>% head() %>% kable()
```
## SEPARATION

Separating  *content* and *region*

```{r separate}
gapminder_long <- gapminder_long %>% 
  separate(cont_region, into=c("continent", "region"), sep="_")
gapminder_long %>% head() %>% kable()
```


## PLOT 

Infant *mortality* vs *fertility* 

```{r plot, warning=FALSE}
library(ggplot2)
ggplot(gapminder, aes(infant_mortality, fertility)) +
  geom_point(alpha= 1/10, color= "blue", size= 1, na.rm= TRUE) +
  xlab(label = "Infant Mortality")+
  ylab(label= "Fertility Rate") +
  ggtitle(label= " Infant Mortality vs Fertility Rate") +
  geom_smooth(method= "lm", se= FALSE, color=" red")
```

From the Plot we can see that there could be a positive correlation between *Infant Mortality* and *Fertility Rate*


So, let's check whether there is this correlation!
```{r correlation}
res <-cor.test(gapminder$infant_mortality, gapminder$fertility, method= "pearson")
res$estimate
```

## References

Irizarry, Rafael A., and Amy Gill. 2021. Dslabs: Data Science Labs. https://CRAN.R-project.org/package=dslabs.




